Torrential Twitter: Climate Change, Female Politicians, and Harassment

### 2024-01-06 Outputs/Presentation/bell_conference_slides.qmd
slides and files

---
title: "Torrential Twitter: Climate Change, Female Politicians, and Harassment"
author: "Inessa De Angelis"
format:
  beamer:
    aspectratio: 169
    theme: Madrid
    colortheme: DarkBlue
    institute: The University of Toronto
    # toc: true
    # Table of contents not generating at the moment
editor: visual
header-includes: 
- \definecolor{DarkBlue}{rgb}{0.05, 0.15, 0.3}
- \setbeamercolor{structure}{fg=DarkBlue}
---

# Introduction

Hello!

------------------------------------------------------------------------

# Slide 2

>>>>

---
title: "Torrential Twitter: Climate Change, Female Politicians, and Harassment"
author: 
  name: "Inessa De Angelis"
  email: "Inessa.DeAngelis@mail.utoronto.ca"
format:
  revealjs
title-slide-attributes: 
  data-background-color: "#CBD6BE"
---

## Background {background-color="#CBD6BE"}
- Harassment on Twitter is well-documented

```{r}
library(tidyverse)
library(knitr)
library(kableExtra)
library(ggplot2)
library(formattable)
library(here)

# Read in the data #
finalized_cleaned_tweets_anon <- read_csv(here::here("Outputs/Data/finalized_cleaned_tweets_anon.csv"))
show_col_types = FALSE

#| message: false
#| eval: true
#| echo: false
#| label: tbl-breakdown
#| tbl-cap: Number of Tweets and their overall percentage of the sample by female politician following the data cleaning process

finalized_cleaned_tweets_anon |>
  group_by(name_of_politician) |>
  count() |>
  ungroup() |>
  mutate(pct = paste0(round((n / sum(n)) * 100), "%")) |>
  arrange(match(name_of_politician, c('Chrystia Freeland', 'Elizabeth May', 'Laurel Collins'))) |>
  kable(
    col.names = c("Name of Politician", "Number of Replies", "Percentage"),
    booktabs = TRUE,
  )

````
